A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-12 manuscript.Rmd
explain how to learn git

<!--I am troubled by how we should recommend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

One of the greatest benefits of open research is that other people can freely reuse your materials.
To use your materials, they first have to find them and learn how to use them.
Interested users find out about your project via the readme.
The readme is the first thing they see when they visit your Project.
It should explain to them what your project is about and how to reproduce your project.
You could for example include the abstract of your (planned) paper here.

>>>>

<!--I am troubled by how we should recommend to learn git-->
Git is can be challenging to learn, because we are used to learn alone and Git is best learned with others.
We recommend to find a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

One of the greatest benefits of open research is that other people can freely reuse materials.
To use your materials, they first have to find them and learn how to use them.
Interested users find out about your project via the readme.
The readme is the first thing they see when they visit your Project.
It should explain to them what your project is about and how to reproduce your project.
You could for example include the abstract of your (planned) paper here.
